Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-20 awipev-CO2.Rmd
Now use sal_insitu_ctd_interp instead of sal_mix_interp

#interpolation of salinity during the FB off maintenance
salinterp <-
  approx(
    d_all$datetime,
    d_all$sal_mix,
    xout = d_all$datetime,
    method = "linear",
    rule = 2
  )
names(salinterp) <- c("datetime", "sal_mix_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_mix_interp <- salinterp$sal_mix_interp

d_all <- d_all %>%
  dplyr::mutate(
    sal_mix_interp =  ifelse(
      datetime > as.POSIXct("2018-03-09 00:00:00") &
        datetime < as.POSIXct("2018-04-16 16:00:00"),
      sal_mix_interp,
      sal_mix
    )
  )

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE, message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)

>>>>

#interpolation of salinity during gaps
salinterp <-
  approx(
    d_all$datetime,
    d_all$sal_insitu_ctd,
    xout = d_all$datetime,
    method = "linear",
    rule = 2
  )
names(salinterp) <- c("datetime", "sal_insitu_ctd_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_interp

d_all <- d_all %>%
  dplyr::mutate(
    sal_insitu_ctd_interp =  ifelse(
      datetime > as.POSIXct("2018-04-16 07:00:00") &
        datetime < as.POSIXct("2018-04-24 22:00:00"),
      sal_insitu_ctd_interp,
      sal_insitu_ctd
    )
  )

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE, message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
